---
title: Colophon
freeze: false
format:
  html:
    knitr:
      opts_chunk:
        dev-args:
          bg: "transparent"
---

```{r}
#| label: packages-functions
#| include: false

library(tidyverse)
library(scales)

show_nice_pal <- function(pal, nrow = 1, show_text = TRUE) {
  out <- tibble(x = 1:length(pal), color = pal) |>
    mutate(color = fct_inorder(color)) |>
    ggplot(aes(x = color, y = 1, fill = color)) +
    geom_tile() +
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_identity() +
    facet_wrap(vars(x), scales = "free_x", nrow = nrow) +
    theme_void(base_family = "Inconsolata") +
    theme(
      panel.spacing.x = unit(-1, units = "pt"),
      panel.spacing.y = unit(-0.5, units = "lines"),
      strip.text = element_blank()
    )

  if (show_text) {
    out <- out +
      theme(
        axis.text.x = element_text(margin = margin(b = 5)),
        panel.spacing.y = unit(0, units = "lines")
      )
  }

  return(out)
}

time_updated <- format(
  lubridate::now(tzone = "America/New_York"),
  "%F at %T US Eastern"
)
```

::: {.dictionary-entry}

[colophon]{.headword} [(noun)]{.part-of-speech}

[col&thinsp;•&thinsp;o&thinsp;•&thinsp;phon&emsp;/ˈkä-lə-fən, -fän/&emsp;/ˈkɒləfən, -fɒn/]{.pronunciation}

1. an inscription at the end of a book or manuscript containing information about its production
2. this page

:::

## Technology

- **Last built**: `{r} time_updated`
- **Software**: Quarto version {{< version >}} and {{< fa brands r-project >}} `{r} R.version$version.string`
- **Hosting**: Hosted at [{{< fa brands github >}} GitHub Pages](https://andrewheiss.github.io/mastering-conjoint-analysis_2026-06/) and built and deployed using [{{< fa brands github >}} GitHub Actions](https://github.com/andrewheiss/mastering-conjoint-analysis_2026-06/blob/main/.github/workflows/publish.yml)


## Design

The typography, colors, and custom CSS settings are all controlled with [this `_brand.yml` file](https://github.com/andrewheiss/mastering-conjoint-analysis_2026-06/blob/main/_brand.yml):

<details>
<summary>Show `_brand.yml` for this site</summary>

```{.yaml filename="_brand.yml"}
{{< include _brand.yml >}}
```

</details>

[(See more about brand.yml [here](https://posit-dev.github.io/brand-yml/)).]{.small}


### Typefaces

I use [Lato](https://en.wikipedia.org/wiki/Lato_(typeface)) [([Google Fonts](https://fonts.google.com/specimen/Lato))]{.small} as the main body font throughout the site, and I use [Aleo](https://alessiolaiso.com/aleo-font){style="font-family: 'Aleo'"} [([Google Fonts](https://fonts.google.com/specimen/Aleo))]{.small} for all headings.

::: {.font-example}
[A heading]{.fake-heading}

Whereas recognition of the *inherent dignity* and of the ***equal and inalienable*** rights of all members of the human family is the foundation of freedom, justice and peace in the world…
:::

### Colors

The colors for this course website come primarily from the ["Tiepolo" palette](https://github.com/BlakeRMills/MetBrewer#tiepolo) from [the {MetBrewer} R package](https://github.com/BlakeRMills/MetBrewer). The colors come from "The Glorification of the Barbaro Family" (1750) by Giovanni Battista Tiepolo.

::: {.column-margin}
![The Glorification of the Barbaro Family, 1750, Giovanni Battista Tiepolo, Italian, [Met link](https://www.metmuseum.org/art/collection/search/437798).](img/tiepolo.jpg){width="100%" fig-align="left"}
:::

```{r}
#| label: show-tiepolo
#| fig-width: 8
#| fig-height: 1
#| out-width: 100%
#| echo: false

MetBrewer::met.brewer("Tiepolo") |> 
  show_nice_pal(show_text = TRUE, nrow = 1)
```


## License and credits

All the materials and content for this course are licensed under [{{< fa brands creative-commons >}} Creative Commons CC-BY-SA {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}}](https://github.com/andrewheiss/mastering-conjoint-analysis_2026-06/blob/main/LICENSE.md).
